Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-07 reports/manuscript/paper.tex
Add model comparisons to elastic net, PCR lasso, and bundle mean lasso

To assess the added value of incorporating anatomical knowledge into our
model, we compared our classification results to those obtained from a lasso
model. The pure lasso model achieved 76\% accuracy and an ROC AUC of 0.76
using the same cross-validation strategy used to assess the SGL model. This
difference in performance justifies the additional complexity of the SGL over
simpler sparsity-inducing regression strategies.

@@

As with ALS classification, we also compared SGL performance with results
obtained using only the lasso penalty. The pure lasso models achieved $R^2 =
0.47$, $0.54$, and $0.70$ for the WH, HBN, and Cam-CAN datasets respectively
using the same cross-validation strategy used to assess the SGL. The SGL
models' performance improvement over lasso is more modest than in the ALS
classification case, which accords with the selected values of the $\alpha$
hyperparameter. These SGL models were more lasso-like in their sparsity
penalties so they are more lasso-like in their predictive performance.

@@

\subsection{Software implementation}

>>>>

To assess the added value of incorporating anatomical knowledge into our
model, we compared our classification results to those obtained from four
other models: a pure lasso model, an elastic net model, a bundle-mean lasso
(i.e. a lasso model trained only on the mean metric values from each bundle),
and a principal components regression lasso (Lasso PCR) model
\cite{powell2018local, rasero2021integrating}. These models achieved
accuracies of 76\%, 76\%, 79.5\%, and 71.5\% respectively and an ROC AUC of
0.76, 0.75, 0.82, and 0.71, respectively using the same cross-validation
strategy used to assess the SGL model. This difference in performance
justifies the additional complexity of the SGL over simpler sparsity-inducing
regression strategies.

@@

As with ALS classification, we also compared SGL performance with results
obtained using the pure lasso, elastic net, bundle-mean lasso, and Lasso PCR.
The pure lasso models achieved $R^2 = 0.47$, $0.54$, and $0.70$ for the WH,
HBN, and Cam-CAN datasets respectively using the same cross-validation
strategy used to assess the SGL. The elastic net models achieved $R^2 =
0.46$, $0.59$, and $0.73$ for the WH, HBN, and Cam-CAN datasets,
respectively. The bundle-mean lasso models achieved $R^2 = 0.33$, $0.22$, and
$0.55$, respectively. And the Lasso PCR models achieved $R^2 = 0.54$, $0.57$,
$0.74$, respectively. The SGL models' performance improvement over lasso is
more modest than in the ALS classification case, which accords with the
selected values of the $\alpha$ hyperparameter. These SGL models were more
lasso-like in their sparsity penalties so they are more lasso-like in their
predictive performance.

@@

\subsection*{Software implementation}
